---
title: "JC24533 postdoc position"
subtitle: "cover letter"
author: |
  | Thomas Huet 
  | mail: <thomashuet7@gmail.com>
  | website: <https://github.com/zoometh/>
date: "12/8/2020"
output: 
  pdf_document:
    keep_tex: true
    includes:
      in_header: preamble.tex
# header-includes:
  # - \hypersetup{colorlinks = false, pdfborder={1 1 1}}
  # - \newcommand{\pkg}[1]{{\fontseries{m}\fontseries{b}\selectfont #1}}
bibliography: bibliography.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(kableExtra)
```

The University of Cambridge opens a fixed-term postdoctoral position, in the framework of the [ERC-funded research project ENCOUNTER](https://www.encounterproject.info/) (PI: Enrico Crema), to assess **cultural boundaries**, **cultural connectivity** and **cultural changes** during the Jōmon-Yayoi transition period.  
 
During more than 10,000 years, Jōmon (16,000–2,800 cal BP) maintain a hunter-gather economy, while the surroundings of the island adopted progressively farming economy [@habu2004ancient]. During the Late Jōmon and Final Jōmon phases (4,420-2,800 cal BP), Southern Yayoi farmers introduced rice and millet to the Japan archipel. The ENCOUNTER project plan to respond to this main question: triggered by the Yayoi demic and cultural-trait diffusion, how the Jōmon culture changes ? To adress this question, multiple lines of evidence coming from Japanese excavation reports (radiocarbon dates, subsistence systems, residiential models, mortuary/ceremonial practices, crafts/trade networks, etc.) and new studies conducted by the project members and key collaborators (organic residues analyses, climatic and landcover restitution, etc.) will be analysed over the **long-term** and at a **large geographical scale** with computational methods.

I am familiar with computational archaeology and computer-based analysis to study archaeological traits over the **long-term** and at a **large geographical scale**. I am used to conduct archaeological researches with formal methods. For example, **cultural boundaries** can be defined as the spatial extent where cultural traits share more between them (intra-variability) than with cultural traits outside this extent (inter-variability). These cultural traits come from different social subsystems (subsistence, technological, demographic, ecological, symbolic) that should be assessed with polythetic/multifactorial analysis and computational methods with descriptive statistics, data mining and statistical test at the temporal and spatial scales. I assume that **cultural connectivity** and **cultural change** should be model with the same statistical means. 

Regarding the **spatial dimension**, data coming from organic residue analysis (WP2), land cover restitution (WP4) and archaeobotanical (WP5) will be processed with map algebra to contrast Jōmo regional responses to the Yayoi economic spreading. I am used to manage spatial analysis such as: sitology, site catchment analysis, shorter paths, inter-visibilities, etc., and to deal with spatial auto-correlation, point pattern analysis, etc. Regarding the **temporal dimension**, it is hard to consider the whole Jōmon period as a unitary culture since, at least, three cycles of population have been percieved [@kobayashi2008jomon]. A great insight will be to parallelized radiocarbon dates summed probability distribution (SPD) with the Jomon well-documented pottery typo-chronology and other cultural-traits [@Habu08; @crema2020multi]. I am familiar with SPDs (see for example the RShiny [EUROEVOL_R app](https://neolithic.shinyapps.io/Euroevol_R/)) and cultural-traits seriations (ie typo-chronology). I am also used to manage interval temporal logic, like Allen's formalism, with computer-based methods. In such a modeling, *events* are considered as `POINTS` when *duration* as considered as `LINES` with a starting *event* (x^-^) and an ending *event* (x^+^). Durations and events can be manage with binary topological relationships (*birel*) and operators like touches/meets, overlaps/intersects, etc.   

I mostly use methods like database/GIS and programmed routines of spatial and non-spatial statistical analysis with \textsf{R}. I also manage networks analysis either for spatial and non-spatial data. In a context of Open Science, open data, and Digital Humanities, I also manage content management system (CMS), GeoCMS, data sharing, data vizualisation with enriched charts and web interactive forms (see the [Golasecca-net webpage](https://zoometh.github.io/golasecca/) for spatial and non-spatial networks, and JSON\_LD serialization). 

I am also able to find, access, interoperate and reuse (FAIR) data, like those published as supplementary material and hosted on the GitHub [***Jomon_SPD_Comparison*** repository](https://github.com/ercrema/jomonPhasesAndPopulation), with near 2,000 radiocarbon dates [@crema2020multi] can be connected, read, calibrated and plotted with \textsf{R} and the packages \pkg{curl} and \pkg{rcarbon} [@Ooms19; @Bevan20]  
&nbsp;
  
```{r dat, fig.height = 4, warning= F}
library(curl) # to connect url
library(rcarbon) # for C14 calibrations
gh.repo <- "https://raw.github.com/ercrema/Jomon_SPD_Comparison/"
gh.c14 <- "master/data/c14dates.csv"
gh.data.c14 <- read.csv(curl(paste0(gh.repo, gh.c14)))
gh.data.c14.sample <- head(gh.data.c14) # first dates
gh.data.c14.sample$ids <- 1:nrow(gh.data.c14.sample)
ages <- calibrate(x = gh.data.c14.sample$C14Age,
                  errors = gh.data.c14.sample$C14Error,
                  calCurves = 'intcal13',
                  ids = gh.data.c14.sample$LabCode,
                  verbose = F)
multiplot(ages, decreasing=TRUE, HPD=TRUE)
```

The geographical counterpart of this radiocarbon dates plot -- with the whole dataset --, made with \textsf{R} and the pakages \pkg{leaflet}, \pkg{htmltools}, \pkg{dplyr} and \pkg{curl}, can be seen on a [GitHub webpage](https://zoometh.github.io/encounter_postdoc/docs/lf_jomon_sites.html).

## Last Words

Archaeological researches over the long-term and at a large scale, like the ENCOUNTER project, integrate large amount of heteroclit data into computational routines. I am used to manage and analyse data with \textsf{R}, GIS and databases, to develop authoring frameworks for data science like RShiny or Rmarkdown documents, Mardown and \LaTeX syntaxes. In a context of Open Science, I also know how to manage open data referencing and online sourcing/publishing.
Regarding the archaeological context -- even I am not familiar with the Japanese prehistory -- I have already an experience on studying acculturation processes like for the Mesolithic-Neolithic transition or the end of the Protohistory in Western Europe. 
Working on the Jōmon-Yayoi transition will allow me to *de-focuse* my current perception of farming/innovation adoption. It would be a great experience for me to developp IT and scientific solutions within the frame of the ENCOUNTER research project and join a team open to innovative methods.

# Reference



